### 2017-10-31 submission/supplemental.Rmd
add stool bray st2

**Table S1: Bray-Curtis Distance Matrix Analyzed by PERMANOVA Adenoma Stool Studies**

@@

@@

@@

```{r supplemental_table3, echo=FALSE, message=FALSE, warning=FALSE}

@@

**Table S3: Summary of Comparisons Based on Additive Treatment Received (Chemotherapy or Chemotherapy and Radiation)**
\footnotesize
```{r supplemental_table4, echo=FALSE, message=FALSE, warning=FALSE}

>>>>

**Table S1: Bray-Curtis Distance Matrix Analyzed by PERMANOVA for Adenoma**

@@

**Table S2: Bray-Curtis Distance Matrix Analyzed by PERMANOVA for Carcinoma**

@@

temp_t2 <- read_csv("../data/process/tables/beta_perm_stool_summary.csv")

table_s2 <- temp_t2 %>% 
  mutate(fstat = round(fstat, digits = 2), 
         r2 = round(r2, digits = 3), 
         pvalue = round(pvalue, digits = 4), 
         study = stringr::str_replace(study, 
                                      c("wang", "weir", "ahn", "zeller", "baxter", "hale", "flemer"), 
                                      c("Wang", "Weir", "Ahn", "Zeller", "Baxter", "Hale", "Flemer")))

colnames(table_s2) <- c("F statistic", "R2", "P-value", "Study", "Carcinoma n", "Control n")

kable(table_s2, format = "markdown", align = 'c', padding = 2)
```

**Table S3: **
\footnotesize
```{r supplemental_table3, echo=FALSE, message=FALSE, warning=FALSE}

@@

```{r supplemental_table, echo=FALSE, message=FALSE, warning=FALSE}

@@
